### 2021-02-25 README.Rmd
release prep

<!-- badges: start -->
[![R build status](https://github.com/ropensci/taxadb/workflows/R-CMD-check/badge.svg)](https://github.com/ropensci/taxadb/actions)
[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![Coverage status](https://codecov.io/gh/ropensci/taxadb/branch/master/graph/badge.svg)](https://codecov.io/github/ropensci/taxadb?branch=master)
[![CRAN status](https://www.r-pkg.org/badges/version/taxadb)](https://cran.r-project.org/package=taxadb)

@@

```{r include=FALSE}
taxadb:::td_disconnect()
MonetDBLite::monetdblite_shutdown()

>>>>

<!-- badges: start -->
[![R build status](https://github.com/ropensci/taxadb/workflows/R-CMD-check/badge.svg)](https://github.com/ropensci/taxadb/actions)
[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://lifecycle.r-lib.org/articles/stages.html)
[![Coverage status](https://codecov.io/gh/ropensci/taxadb/branch/master/graph/badge.svg)](https://codecov.io/github/ropensci/taxadb?branch=master)
[![CRAN status](https://www.r-pkg.org/badges/version/taxadb)](https://cran.r-project.org/package=taxadb)
[![DOI](https://zenodo.org/badge/130153207.svg)](https://zenodo.org/badge/latestdoi/130153207)

@@

```{r include=FALSE}
taxadb:::td_disconnect()
